Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex
maketitle change
fixed slight errors in peter adding back my ssec

\begin{defn}
\label{defn:grlex}
If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
\succ_{\text{grlex}} \beta$ if either $\alpha$ has larger degree:
\begin{equation}
\deg \alpha := \sum_{i = 1}^{n} d f_i  > \sum_{i = 1}^{n} d f_i' =: \deg \beta
\end{equation}
or $\alpha$ is larger using the lexicographical ordering event of equal
degrees:

@@

We can equip the polynomial ring $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$
-with the (weighted graded) reverse lexicographic order
-\textbf{grevlex} $\prec_{\text{grevlex}}$ as follows:
-
-\begin{defn}
-\label{defn:grevlex}
-If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
-^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
-monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
-\succ_{\text{grevlex}} \beta$ if either $\alpha$ has larger degree:
-
-\begin{equation}
-	\deg \alpha := \sum_{i = 1}^{n} d f_i  > \sum_{i = 1}^{n} d f_i' =: \deg \beta
-\end{equation}
-or $\alpha$ has a smaller right-most entry in the event of equal
-degrees:
-
-\begin{equation}
-\label{eqn:grevlex-tie}
-	\deg \alpha = \deg \beta \text{ and }	f_i - f_i' < 0 \text{ for
-the	largest } i \text{ such that } f_i \neq f_i'
-\end{equation}
-\end{defn}

@@

\noindent
so $R'$ must have some generators $x_{3, 1}, x_{5, 1}, x_{7, 1},
x_{7, 2}$ with $x_{i,j} \in H^0(\sx', i K_{\sx'})$.

>>>>

\begin{defn}
\label{defn:grlex}
If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
\succ_{\text{grlex}} \beta$ if either $\alpha$ has larger degree:

\begin{equation}
	\deg \alpha := \sum_{i = 1}^{n} d f_i  > \sum_{i = 1}^{n} d f_i' =: \deg \beta
\end{equation}
or $\alpha$ is larger using the lexicographical ordering event of equal
degrees:

@@

@@

\noindent
so $R'$ must have some generators $x_{3, 1}, x_{5, 1}, x_{7, 1},
x_{7, 2}$ with $x_{i, j} \in H^0(\sx', i K_{\sx'})$.
